---
title: "R Code"
author: "Daniel Davieau"
date: "February 3, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#### Problem 2b
#####Wilcoxon rank sum test
```{r}
Logged = c(85.6 ,85.4 ,75.5 ,53.1 ,46.7 ,45 ,43.2 ,40.8 ,18.2)
Notlogged = c(56.1 ,34.2 ,23.6 ,18.1 ,13.3 ,-8.1 ,-20.1)
wilcox.test(Logged,Notlogged, correct=TRUE)
```
#####Calculate Confidence Interval
```{r}
sum(rank(c(Logged,Notlogged))[1:9])
sum(rank(c(Logged,Notlogged))[10:16]) #Sum ranks not Logged
```
#### Problem 3e
```{r}
library(readr)
EducationData <- read_csv("EducationData.csv", 
    col_types = cols(Subject = col_skip()))
t.test(EducationData$Income2005 ~ EducationData$Educ, data=EducationData, 
       var.equal=FALSE,
       conf.level=0.95)
```
#### Problem 5e
```{r}
## Two-sample test.
## Hollander & Wolfe (1973), 69f.
## Permeability constants of the human chorioamnion (a placental
##  membrane) at term (x) and between 12 to 26 weeks gestational
##  age (y).  The alternative of interest is greater permeability
##  of the human chorioamnion for the term pregnancy.
x <- c(85 ,70 ,40 ,65 ,80 ,75 ,55 ,20 ,70)
y <- c(75 ,50 ,50 ,40 ,20 ,65 ,40 ,25 ,30)
wilcox.test(x, y, alternative = "g")    
wilcox.test(x, y, alternative = "greater",
            exact = FALSE, correct = FALSE)
                                           
wilcox.test(rnorm(9), rnorm(9, 2), conf.int = TRUE)
